I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-11-04 submission/paper.tex
Started work on introduction and conclusion sections

\title{I don't know, are you sure we want to do this?\
Sea level adaptation decisions under uncertainty}

@@

In this paper we illustrate the uncertainty of sea level projections, and combine this with the a simplified decision problem where planners want to know how early they should implement costly adaptation measures.

@@

@@

We will instead use the empirical approach of Rahmstorf and collaborators \citep{Rahmstorf07,Rahmstorf11}, employing the statistical modeling of \citet{Bolin2014a} to relate global annual mean temperature anomalies \citep{giss} to global mean sea level anomalies \citep{csiro}.

@@

\section{Decision tools {\color{blue} (KdB, MD, TT)}}

@@

\section{Case studies}

@@

\section{Conclusions}

>>>>

\title{I don't know, are you sure we want to do this?\\
Sea level adaptation decisions under uncertainty}

@@

In this paper we illustrate the uncertainty of sea level projections, and combine this with a simplified decision problem where planners want to know how early they should implement costly adaptation measures.

Section \ref{sealevelproj} describes our approach to projecting sea level. In section \ref{decision_tools} we describe the type of decision problem that we are going to attack. We apply these tools to a sea level projection for Bergen, Norway, %and for Esbjerg, Denmark 
in section \ref{cases}.  In the final section \ref{unc}  we demonstrate the consequences of ignoring the uncertainty in the projections.

@@

\label{sealevelproj}

@@

We will instead use the empirical approach of Rahmstorf and collaborators \citep{Rahmstorf07,Rahmstorf11}, employing the statistical modeling of \citet{Bolin2014a} to relate global annual mean temperature anomalies to global mean sea level anomalies.

@@

\section{Decision tools {\color{blue} (KdB, MD, TT)}}
\label{decision_tools}

@@

\section{Case studies}
\label{cases}

@@

\section{The value of including uncertainty}
\label{unc}

In many cases sea level rise projections are given as a single number for each scenario, usually the mean or median of the ensemble of projections from different climate models (e.g. \citet{climateimpactgroup}). Sometimes the spread of the ensemble is used to assess the uncertainty in the projections (e.g., the Norwegian Environmental Agency recommends using the upper ensemble value for RCP 8.5 as the basis for planning decision, pers. comm. from Even Nilsson, Norwegian Mapping Authority). In our analysiis there are two more sources of uncertainty, namely the two regression models. Figure \ref{fig:unc} shows the single number (vertical black line), the ensemble spread (histogram), the uncertainty including the global model (red) and the full uncertainty (blue) for Bergen projections of sea level rise relative to 1999 under RCP 8.5.

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{unc.pdf}
\caption{2050 Bergen sea level projections with uncertainty due to different sources for RCP 8.5. The black line is the median projection (with no uncertainty), while the grey histogram corresponds to the spread of the climate models, the red curve adds the uncertainty due to the relation between global temperature and global sea level, and the blue line that due to downscaling global sea level to Bergen. } 
\label{fig:unc}
\end{center}
\end{figure}
